% Ross_Guarino_Resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
% (c) 2012 William M. Ziener-Dignazio <slackwill@csh.rit.edu> http://csh.rit.edu/~slackwill
% (c) 2014 Ross L. Guarino <rssguar@gmail.com> http://rlguarino.com
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links 
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\restwoheading}[2]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		{#3} & {#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\restwosubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document} 

\thispagestyle{empty}
\pagestyle{empty}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r} \\
	\textbf{\href{http://www.rlguarino.com/}{\large Ross L. Guarino}} & \href{mailto:rlguarino@gmail.com}{rssguar@gmail.com}\\ &
	\href{http://rlguarino.com/}{rlguarino.com} \\ \vspace{-10mm} \\
	{\footnotesize {{Current: 230 Hendrix Ave, Apartment 12,
West Henrietta, NY 14586}}} & \\
	{\footnotesize {{Home: 285 Crosby Ave, Kenmore, NY 14217}}} & \\
	{\footnotesize {{Phone: (716) 982-2597}}} 	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Objective}
{
	\begin{itemize}
	\setlength\itemsep{0em}
		\footnotesize
		\item{Obtain full time position or cooperative study for a minimum of 3 months}
		\item{A position of Software Engineer or equivalent}
		\item{To research, design, and implement solutions for real world problems}
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%

\resheading{Professional Experience}
{\footnotesize
	\begin{itemize}
		\item
                        \ressubheading{Google Inc.}{\href{http://www.google.com/}{google.com}}{Site Reliability Engineer - Intern}{May - August 2015}
                        { \footnotesize
                                \begin{itemize}
                                  \item{Fault Injection and Disaster Recovery Tools}
                                \end{itemize}
                        }

               \item
                        \ressubheading{Ntid}{\href{http://www.ntid.rit.edu/}{ntid.rit.edu}}{Backend Software Engineer}{June 2014 - May 2015}
                        { \footnotesize
                                \begin{itemize}
                                  \item{Developed a web application for use by over 300 interpreters to track and managed their activities}
                                  \item{Designed and implemented RESTFul API in python. }
                                  \item{Developed a API in python using API best practices}
                                \end{itemize}
                        }


	       \item
			\ressubheading{Exablox}{\href{http://www.exablox.com/}{exablox.com}}{Continuous Integration - Intern}{June 2013 - January 2014}
			{ \footnotesize
				\begin{itemize}
                                  \item{Developed internal developer resource and continuous integration systems}
				  \item{Designed and implemented a system to manage and test data}
				  \item{Developed a Buildbot and ReviewBoard collaboration plugin in Python}
				\end{itemize}
			}
	\end{itemize}  % End Experience list
}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Projects}
{ \footnotesize
	\textit{Many Available on {\href{http://www.github.com/rlguarino/}{github.com/rlguarino}}}
	\begin{itemize}
          \item
            \restwosubheading{Intelligent Scan Detection}{Go, Python}
            \begin{itemize}
              \item{An intelligent security system designed to detect and respond to port scans.}
              \item{Uses a neural network to classify traffic data as potential scans in real time. }
              \item{Generated realistic traffic data using a process of categorizing traffic characteristics and composing fake traffic on demand.}
            \end{itemize}

           \item 
	     \restwosubheading{Unitracker }{Go}
	     \begin{itemize}
		\item{A continuous integration unit test tracking system built with go.}
                \item{Designed to be used as part of a buildbot system the Unitracker will track and display the outcome of unit tests in a easy to understand manner.}
	     \end{itemize}
	    \item		
	      \restwosubheading{Taskboard}{Go}
	      \begin{itemize}
		\item{A web application designed to interface with{\href{http://csh.rit.edu}{Computer Science House} } systems to provide a way for members to pay each other to complete tasks using a special currency.} 
	      \end{itemize}
	    \item
	       \restwosubheading{PyShare}{Python}
	       \begin{itemize}
		 \item{A peer-to-peer file sharing program}
                 \item{Implemented my own Diffie-Hellman encryption to secure the traffic}
	       \end{itemize}
	    \item		
	      \restwosubheading{Smart Vending Machine System}{Java}
	      \begin{itemize}
		\item{A smart vending machine system group project for a Software Engineering class.}
                \item{Networked vending machine systems with an inventory management system and real time system monitoring}
	      \end{itemize}
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	{ \footnotesize
	\begin{itemize}
		\item
			\ressubheading{Rochester Institute of Technology - New York}{\href{http://www.rit.edu}{rit.edu}}{\href{http://www.cs.rit.edu/}{Undergraduate Computer Science Student}}{Aug. 2011 - Present}
				{ \footnotesize
				\begin{itemize}
					\item{Expected Graduation Date: June 2016}
					\item{Core Courses:}
						\begin{itemize}
							\item{Computer Organization}
							\item{Computer Science[1-4]}
                                                        \item{Intelligent Security Systems}
							\item{Concepts of Parallel \& Distributed Systems}
							\item{Data Communications}
						\end{itemize}
				\end{itemize}
				}
	\end{itemize} % End Education list
	}


%%%%%%%%%%%%%%%%%%%%%%

\resheading{{Skills}}
{ \footnotesize
		\begin{itemize}
			\item{Languages: Assembly (MIPS), C, GoLang, Java, Python}
			\item{Tools: Emacs, Git, LaTex, Subversion, Vi/Vim, Docker}
			\item{Concepts: Parallel \& Distributed Systems, Systems Programming, Intelligent Systems}
		\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Online Presence}
{
	\begin{tabularx}{2in}{XX}
		LinkedIn: & \href{http://www.linkedin.com/in/rlguarino/}{www.linkedin.com/in/rlguarino/} \\
		Githhub: & \href{http://www.github.com/rlguarino}{github.com/rlguarino} \\
		Blog: & \href{http://www.rlguarino.com/}{rlguarino.com} \\
		Twitter: & \href{https://twitter.com/rlguarino}{twitter.com/rlguarino} \\
	\end{tabularx}
}
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%

\end{document}


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html
